Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-04-10 main.tex
Edit/response to APT

A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC, \LOWSEC\} \times \{\HIGHINT, \LOWINT\}$ is a map from
machine components to a pair of confidentiality and integrity labels.
$\LOWSEC$ marks locations whose contents represent data observable
{\em by the current process}; $\HIGHSEC$ corresponds to non-observable
data (e.g. local state of the process caller). $\HIGHINT$ marks
locations that the current process does not have write access to;
$\LOWINT$ is freely accessible \apt{``accessible''?} memory. As examples of different
combinations consider the following:
\begin{itemize}
\item Locations that belong to the current process such as
  available registers, local stack, memory accessible through
  available pointers will be tagged $\LOWSEC \times \LOWINT$:
  they can be both read and written.
\item The local state of the caller that needs to be protected from a
  potentially untrusted callee will be marked $\HIGHSEC \times
  \HIGHINT$. The callee should be able to neither read nor write
  these locations.
\item The instruction memory is read only for every process: $\LOWSEC
  \times \HIGHINT$.
\item We won't have examples of secret data that can be overwritten.
  \leo{Maybe in the lazy setting?}
\end{itemize}

@@

\apt{How is this definition of contoured traces connected to the various properties
  below (which seem to talk about an (uncontoured) trace plus a single contour) ?}

>>>>

A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC, \LOWSEC\} \times \{\HIGHINT, \LOWINT\}$ is a map from
machine components to a pair of confidentiality and integrity labels.
$\LOWSEC$ marks locations whose contents represent data observable
{\em by the current process}; $\HIGHSEC$ corresponds to non-observable
data (e.g. local state of the process caller). $\HIGHINT$ marks
locations that the current process does not have write access to;
$\LOWINT$ is writeable. As examples of different
combinations consider the following:
\begin{itemize}
\item Locations that belong to the current process such as
  available registers, local stack, memory accessible through
  available pointers will be tagged $\LOWSEC \times \LOWINT$:
  they can be both read and written.
\item The local state of the caller that needs to be protected from a
  potentially untrusted callee will be marked $\HIGHSEC \times
  \HIGHINT$. The callee should be able to neither read nor write
  these locations.
\item The instruction memory is read only for every process: $\LOWSEC
  \times \HIGHINT$.
\item We won't have examples of secret data that can be overwritten.
  \leo{Maybe in the lazy setting?}
\end{itemize}

@@

\apt{How is this definition of contoured traces connected to the various properties
  below (which seem to talk about an (uncontoured) trace plus a single contour) ?}
\leo{It only appears in the $C_i$ part of the stack safety property}
